WORCS: A Workflow for Open Reproducible Code in Science

### 2020-10-28 paper/Manuscript_DS.Rmd
Add docker file

---
author:
  - name: Caspar J. van Lissa
    affiliation: 'Utrecht University'
    address: Padualaan 14, 3584CH Utrecht, The Netherlands
    email: c.j.vanlissa@uu.nl
  - name: Andreas M. Brandmaier
    affiliation: 'Max Planck Institute'
  - name: Loek Brinkman
    affiliation: 'UMC Utrecht'
  - name: Anna-Lena Lamprecht
    affiliation: 'Utrecht University'
    email: a.l.lamprecht@uu.nl
  - name: Aaron Peikert
    affiliation: Max Planck Institute
  - name: Marijn E. Struiksma
    affiliation: 'Utrecht University'
  - name: Barbara Vreede
    affiliation: 'Utrecht University'
title: "WORCS: A Workflow for Open Reproducible Code in Science"
short:      "WORKFLOW FOR OPEN SCIENCE"
abstract: |
  Adopting open science
  principles can be challenging and time-intensive, because doing so requires
  substantial conceptual education and training in the use of new tools.
  This paper introduces the Workflow for
  Open Reproducible Code in Science (WORCS): A step-by-step
  procedure that researchers can follow to make a research project open and
  reproducible, accompanied by an open source software implementation that 
  automates these steps.
  The 
  purpose of the workflow is to lower the threshold for 
  adoption of open science principles. 
  It is based on best practices, and can be used either in
  parallel to, or in absence of, top-down requirements by journals,
  institutions, and funding bodies.
  This workflow is primarily targeted towards
  scholars working in R on a private computer,
  conducting research that involves academic prose, analysis code,
  and (optionally) tabular data - but it is flexible enough to accommodate many
  other scenarios.
  To facilitate widespread adoption, the
  WORCS principles are implemented in the R package `worcs`, which offers an
  RStudio 
  project template that is, effectively, a "one-click solution" for R users,
  and utility functions for specific workflow steps.
  This paper addresses the design of the workflow,
  discusses how it meets different 
  standards for open science, and provides examples of the implementation of
  `worcs` in `R`. All source code for the `R` package,
  and replication materials for the manuscript, are available at 
  https://github.com/cjvanlissa/worcs.
authornote: "blabla"
keywords:
  # at least one keyword must be supplied
  formatted: [open science, reproducibility, r, dynamic document generation, version control]
  plain:     [open science, reproducibility, r, dynamic document generation, version control]
preamble: >
  \usepackage{amsmath}
bibliography      : ["worcs.bib"]  
urlcolor          : blue
output: rmarkdown::html_document
knit: worcs::cite_all
---

>>>>

---
author:
  - name: Caspar J. van Lissa
    affiliation: 'Utrecht University'
    address: Padualaan 14, 3584CH Utrecht, The Netherlands
    email: c.j.vanlissa@uu.nl
  - name: Andreas M. Brandmaier
    affiliation: 'Max Planck Institute'
  - name: Loek Brinkman
  - name: Anna-Lena Lamprecht
    affiliation: 'Utrecht University'
    email: a.l.lamprecht@uu.nl
  - name: Aaron Peikert
    affiliation: Max Planck Institute
  - name: Marijn E. Struiksma
    affiliation: 'Utrecht University'
  - name: Barbara Vreede
    affiliation: 'Utrecht University'
title: "WORCS: A Workflow for Open Reproducible Code in Science"
short:      "WORKFLOW FOR OPEN SCIENCE"
shorttitle:      "WORKFLOW FOR OPEN SCIENCE"
abstract: |
  Adopting open science
  principles can be challenging and time-intensive, because doing so requires
  substantial conceptual education and training in the use of new tools.
  This paper introduces the Workflow for
  Open Reproducible Code in Science (WORCS): A step-by-step
  procedure that researchers can follow to make a research project open and
  reproducible, accompanied by an open source software implementation that 
  automates these steps.
  The 
  purpose of the workflow is to lower the threshold for 
  adoption of open science principles. 
  It is based on best practices, and can be used either in
  parallel to, or in absence of, top-down requirements by journals,
  institutions, and funding bodies.
  This workflow is primarily targeted towards
  scholars working in R on a private computer,
  conducting research that involves academic prose, analysis code,
  and (optionally) tabular data - but it is flexible enough to accommodate many
  other scenarios.
  To facilitate widespread adoption, the
  WORCS principles are implemented in the R package `worcs`, which offers an
  RStudio 
  project template that is, effectively, a "one-click solution" for R users,
  and utility functions for specific workflow steps.
  This paper addresses the design of the workflow,
  discusses how it meets different 
  standards for open science, and provides examples of the implementation of
  `worcs` in `R`. All source code for the `R` package,
  and replication materials for the manuscript, are available at 
  https://github.com/cjvanlissa/worcs.
authornote: "blabla"
keywords:
  # at least one keyword must be supplied
  formatted: [open science, reproducibility, r, dynamic document generation, version control]
  plain:     [open science, reproducibility, r, dynamic document generation, version control]
preamble: >
  \usepackage{amsmath}
bibliography      : ["worcs.bib"]  
urlcolor          : blue
output: rmarkdown::html_document
knit: worcs::cite_all
---
